---
title: "Lab11"
author: "Jason Chen"
date: "2024-11-07"
output: 
  html_document:
    toc: true
    toc_float: true
---

# Task 1
```{r}
  getwd()
```

# Task 2

## R as calculator
```{r}
  d=c(5.0581, 4.9707, 5.0893, 4.9334, 4.9777, 5.0285, 4.8555, 4.9565, 
4.9769, 4.9722, 4.999, 4.9925, 4.9686, 5.0662, 4.9239, 4.9781, 
5.0485, 5.0014, 4.9957, 5.0195, 5.0118, 4.9928, 5.0361, 5.0185, 
4.9879)

  t1=qt(1-(0.05/2),24)
  ci=c()
  ci[1]=mean(d)-t1*sd(d)/sqrt(25)
  ci[2]=mean(d)+t1*sd(d)/sqrt(25)
  ci
  
  t2=qt(1-(0.10/2),24)
  ci[1]=mean(d)-t2*sd(d)/sqrt(25)
  ci[2]=mean(d)+t2*sd(d)/sqrt(25)
  ci
  
  t3=qt(1-(0.20/2),24)
  ci[1]=mean(d)-t3*sd(d)/sqrt(25)
  ci[2]=mean(d)+t3*sd(d)/sqrt(25)
  ci
  
  t4=qt(1-(0.5/2),24)
  ci[1]=mean(d)-t4*sd(d)/sqrt(25)
  ci[2]=mean(d)+t4*sd(d)/sqrt(25)
  ci
```

## Use t.test()
```{r}
  obj=t.test(d,conf.level=0.80)
  obj$conf.int
```

## $\sigma^2$ using R
```{r}
  t1=qchisq(1-(0.05/2),24)
  t1a=qchisq(0.05/2,24)
  ci[1]=(24*sd(d)^2)/t1
  ci[2]=(24*sd(d)^2)/t1a
  ci
  
  t2=qchisq(1-(0.10/2),24)
  t2a=qchisq(0.10/2,24)
  ci[1]=(24*sd(d)^2)/t2
  ci[2]=(24*sd(d)^2)/t2a
  ci
  
  t3=qchisq(1-(0.20/2),24)
  t3a=qchisq(0.20/2,24)
  ci[1]=(24*sd(d)^2)/t3
  ci[2]=(24*sd(d)^2)/t3a
  ci
  
  t4=qchisq(1-(0.50/2),24)
  t4a=qchisq(0.50/2,24)
  ci[1]=(24*sd(d)^2)/t4
  ci[2]=(24*sd(d)^2)/t4a
  ci
```

# Task 3

## $\mu_1-\mu_2$
```{r}
  blue=c(21.65, 17.48, 20.1, 21.57, 14.82, 19.17, 21.08, 18.23, 22.93, 
15.66, 20.89, 21.66, 18.5, 20.59, 18.63, 18.91, 19.53, 17.7, 16.5, 19.03)
	snapper=c(31.65, 27.48, 30.1, 31.57, 24.82, 29.17, 31.08, 28.23, 32.93, 
25.66, 30.89, 31.66, 28.5, 30.59, 28.63)
	
  n1=length(blue)
  n2=length(snapper)
  
  spsq=((n1-1)*var(blue)+(n2-1)*var(snapper))/(n1+n2-2)
  t=qt((1-(0.05/2)),n1+n2-2)
  
  
  ci[1]=mean(blue)-mean(snapper)-t*sqrt(spsq*(1/n1+1/n2))
  ci[2]=mean(blue)-mean(snapper)+t*sqrt(spsq*(1/n1+1/n2))
  ci
  
  
  n1=length(snapper)
  n2=length(blue)
  
  spsq=((n1-1)*var(snapper)+(n2-1)*var(blue))/(n1+n2-2)
  ci[1]=mean(snapper)-mean(blue)-t*sqrt(spsq*(1/n1+1/n2)) 
  ci[2]=mean(snapper)-mean(blue)+t*sqrt(spsq*(1/n1+1/n2))
  ci
```

The confidence interval shows that about 95% of the average length of snappers were 8.757585 to 11.840749 inches longer than blue cod bass.

## Using t.test()
```{r}
  t.test(snapper,blue,conf.level = 0.95,var.equal = TRUE)$conf.int
  t.test(snapper,blue,conf.level = 0.85,var.equal = TRUE)$conf.int
  t.test(snapper,blue,conf.level = 0.75,var.equal = TRUE)$conf.int
  t.test(snapper,blue,conf.level = 0.25,var.equal = TRUE)$conf.int
```

The interval becomes smaller and closer to each other as the confidence level increases.

# Task 4

## Paired samples
```{r}
  Exam1=c(40.98, 59.36, 46.69, 41.8, 61.63, 65.31, 62.96, 60.21, 56.89, 
78.41, 53.44, 75.2, 60.54, 52.43, 41.41, 70.79, 73.55, 55.65, 
61.43, 63.84, 58.07, 53.79, 54.45, 67.18, 44.46)
  Exam2=c(50.22, 66.19, 58.75, 51.88, 66.61, 70.86, 74.25, 70.23, 69.55, 
87.18, 63.62, 81.7, 70.5, 66.02, 51.35, 80.92, 85.65, 65.44, 
74.37, 75.28, 67.86, 59.92, 64.42, 73.57, 57.15)
  n=length(Exam1)
  exdif=Exam1-Exam2
  t.test(exdif,conf.level=0.95)$conf.int
```

The confidence interval shows that 95% of the average Exam1 scores were lower than the average Exam2 scores within the range of (-10.731329, -8.710271).

## t.test() with other intervals
```{r}
  t.test(exdif,conf.level=0.90)$conf.int
  t.test(exdif,conf.level=0.80)$conf.int
  t.test(exdif,conf.level=0.70)$conf.int
  t.test(exdif,conf.level=0.60)$conf.int
  t.test(exdif,conf.level=0.10)$conf.int
```

# Task 5
```{r}
  bird<-read.csv("NZBIRDS.csv")
  names(bird)
  addmargins(with(bird, table(Extinct, Flight)))
  
  n1=38
  n2=78
  fless1=21
  fless2=7
  
  p1=fless1/n1
  p2=fless2/n2
  
  sq=sqrt((p1*(1-p1)/n1)+(p2*(1-p2)/n2))
  z=qnorm(1-(0.05/2))
  ci[1]=(p1-p2)-z*sq
  ci[2]=(p1-p2)+z*sq
  ci
```

# Task 6

## Ratio of two population variances
```{r}
  set.seed(35);sam1=rnorm(25,mean=10,sd=5)
  set.seed(45);sam2=rnorm(34,mean=40,sd=8)
  
  s1=var(sam1)
  s2=var(sam2)
  
  n1=length(sam1)
  n2=length(sam2)
  
  low<-qf(0.05/2,n1-1,n2-2)
  up<-qf((1-(0.05/2)),n2-1,n1-2)
  
  ci[1]=(s1/s2)/low
  ci[2]=(s1/s2)*up
  ci
```
## USe var.test()
```{r}
  var.test(sam1,sam2,conf.level = 0.80)$conf.int
  var.test(sam1,sam2,conf.level = 0.70)$conf.int
  var.test(sam1,sam2,conf.level = 0.60)$conf.int
  var.test(sam1,sam2,conf.level = 0.50)$conf.int
```

# Task 7
```{r}
  set.seed(23);x = rnorm(30,mean=10,sd=12)
  MATH4753JChen::myci(x)
```
